Simulating DeLosh 1997

### 2023-05-23 Model/group_fits.qmd
test

---
title: ALM & EXAM Fitting
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: false
---

### Prep data
```{r}
#| code-fold: show
pacman::p_load(tidyverse,data.table)
options(dplyr.summarise.inform=FALSE)

d <- readRDS('dPrune-01-19-23.rds')

dtest <- d %>% filter(expMode %in% c("test-Nf","test-train-nf")) %>% group_by(id,lowBound) %>% 
  mutate(nBand=n(),band=bandInt,id=factor(id)) %>% group_by(id) %>% mutate(nd=n_distinct(lowBound))
# unique(dtest[dtest$nd==4,]$sbjCode) # 7 in wrong condition
dtest <- dtest %>% group_by(id,lowBound) %>% filter(nBand>=5 & nd==6)
# for any id that has at least 1 nBand >=5, remove all rows with that id. 
dtest <- dtest %>% group_by(id) %>% filter(!id %in% unique(dtest$id[dtest$nBand<5]))

@@

ds <- d %>% filter(expMode %in% c("train","train-Nf","test-Nf","test-train-nf")) %>% 
filter(!id %in% unique(dtest$id[dtest$nBand<5])) %>% 
select(id,condit,catOrder,feedbackType,expMode,trial,gt.train,vb,band,bandInt,lowBound,highBound,input,vx,dist,vxb)

dst <- ds %>% filter(expMode=="train",catOrder=="orig")

@@

>>>>

---
title: Group Level Fits
date: last-modified
categories: [Modeling, ALM, R]
page-layout: full
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: false
---

### Prep data
```{r}
#| eval: true
#| code-fold: show
pacman::p_load(tidyverse,data.table,here)
options(dplyr.summarise.inform=FALSE)

d <- readRDS(here("data/dPrune-01-19-23.rds"))
dtest <- d %>% filter(expMode %in% c("test-Nf","test-train-nf")) %>% group_by(id,lowBound) %>% 
  mutate(nBand=n(),band=bandInt,id=factor(id)) %>% group_by(id) %>% mutate(nd=n_distinct(lowBound))
# unique(dtest[dtest$nd==4,]$sbjCode) # 7 in wrong condition
dtest <- dtest %>% group_by(id,lowBound) %>% filter(nBand>=5 & nd==6)
# for any id that has at least 1 nBand >=5, remove all rows with that id. 
dtest <- dtest %>% group_by(id) %>% filter(!id %in% unique(dtest$id[dtest$nBand<5]))

@@

ds <- d %>% filter(expMode %in% c("train","train-Nf","test-Nf","test-train-nf")) %>% 
filter(!id %in% unique(dtest$id[dtest$nBand<5])) %>% 
select(id,condit,catOrder,feedbackType,expMode,trial,gt.train,vb,band,bandInt,lowBound,highBound,input,vx,dist,vxb) 
head(ds)

dst <- ds %>% filter(expMode=="train",catOrder=="orig")
head(dst)
colnames(dst)

@@

head(dst)
dst[1:2,]

### 2023-05-23 Simulations/DeLosh97_Sim.qmd
test

---
title: Simulating DeLosh 1997
code-fold: true
code-tools: true
execute: 
  warning: false
---

@@

lowDensityTrainBlock <- c(30.5, 36.0, 41.0, 46.5, 53.5, 59.0, 64.0, 69.5)
medDensityTrainBlock <- c(
    30.0, 31.5, 33.0, 34.5, 36.5, 38.5, 41.0, 43.5, 46.0,
    48.5, 51.5, 54.0, 56.5, 59.0, 61.5, 63.5, 65.5, 67.0, 68.5, 70.0
)
highDensityTrainBlock <- c(
    30.0, 30.5, 31.0, 32.0, 33.0, 33.5, 34.5, 35.5,
    36.5, 37.0, 38.0, 38.5, 39.5, 40.5, 41.5, 42.0, 43.0,
    43.5, 44.5, 45.5, 46.5, 47.0, 48.0, 48.5, 49.0, 51.0, 51.5, 52.0,
    53.0, 53.5, 54.5, 55.5, 56.5, 57.0, 58.0, 58.5, 59.5, 60.5, 61.5, 
    62.0, 63.0,63.5, 64.5, 65.5, 66.5, 67.0, 68.0, 69.0, 69.5, 70.0
)
# low density has 25 training blocks, medium has 10 blocks, high has 4 blocks.

>>>>

---
title: Simulating DeLosh 1997
date: last-modified
categories: [Simulation, ALM, EXAM, R]
code-fold: true
code-tools: true
execute: 
  warning: false
---

@@

lowDensityTrainBlock <- c(30.5, 36.0, 41.0, 46.5, 53.5, 59.0, 64.0, 69.5)
medDensityTrainBlock <- c(
    30.0, 31.5, 33.0, 34.5, 36.5, 38.5, 41.0, 43.5, 46.0,
    48.5, 51.5, 54.0, 56.5, 59.0, 61.5, 63.5, 65.5, 67.0, 68.5, 70.0
)
highDensityTrainBlock <- c(
    30.0, 30.5, 31.0, 32.0, 33.0, 33.5, 34.5, 35.5,
    36.5, 37.0, 38.0, 38.5, 39.5, 40.5, 41.5, 42.0, 43.0,
    43.5, 44.5, 45.5, 46.5, 47.0, 48.0, 48.5, 49.0, 51.0, 51.5, 52.0,
    53.0, 53.5, 54.5, 55.5, 56.5, 57.0, 58.0, 58.5, 59.5, 60.5, 61.5, 
    62.0, 63.0,63.5, 64.5, 65.5, 66.5, 67.0, 68.0, 69.0, 69.5, 70.0
)
# all density conditions have the same # of training trials, but differ in the # of repetitions per items, or blocks,  low density has 25 training blocks, medium has 10 blocks, high has 4 blocks.
